%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {DevOps Consultant - Contract} % Job title
    {Immersive Gamebox} % Organization
    {London, United Kingdom - Remote} % Location
    {Sept. 2022 - } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engineered an automated deployment ecosystem using \textbf{Terraform, Ansible, Packer, and Jenkins} for Immersive Gamebox's central AWS systems and expanding on-premise hardware across multiple venues. This scalable solution played a pivotal role in enabling rapid expansion while maintaining impeccable infrastructure consistency}
        \item {Built a sophisticated multi-transit gateway private network, optimized for low-latency communication among Immersive Gamebox's international venues. Leveraging Terraform, this dynamic network architecture facilitates the seamless addition of new venues}
        \item {Successfully orchestrated the migration of all applications from Elastic Beanstalk to AWS ECS, bolstering reliability and scalability. Implemented comprehensive CI/CD pipelines through GitHub Actions, streamlining the deployment process and ensuring consistent, efficient releases}
        \item {Provided strategic technical consultancy directly to the CTO, offering insights and guidance that contributed to informed decision-making. Recognized as a point of escalation for complex technical issues, demonstrating your expertise as a dependable problem solver and enhancing operational effectiveness}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer and AWS Consultant - Contract} % Job title
    {MeetMyna} % Organization
    {London, United Kingdom - Remote} % Location
    {Jun. 2022 - Sept. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Pioneered the development of an innovative \textbf{Cloud Native SaaS} offering for MeetMyna's products as the sole engineer on the project. Seamlessly integrated existing voice technology using \textbf{React (TypeScript)}, \textbf{AWS Lambda (TypeScript)}, \textbf{AWS DynamoDB}, AWS API Gateway, and AWS Cognito, amplifying the company's capabilities in the small/medium buiness sector}
        \item {Leveraged the power of the \textbf{Serverless Framework} to architect and build a robust and scalable solution}
        \item {Demonstrated expertise in third-party API integration by seamlessly linking the solution with key platforms including Zoom, Stripe, Dropbox, and Microsoft Teams}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior DevOps Engineer \& Consultant - Contract} % Job title
    {Experity} % Organization
    {Chicago, United States - Remote} % Location
    {May. 2020 - May. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Orchestrated the successful transition of Experity's infrastructure to \textbf{AWS} from on premise VMWare, delivering expert consultancy on multi-account management, network optimization, and streamlined application deployment, optimising operational efficiency within the healthcare sector.}
        \item {Architected and managed \textbf{EKS} clusters utilising \textbf{Terraform} across multiple-regions, overseeing the comprehensive configuration of applications, operators, and controllers}
        \item {Spearheaded a cross-functional team in the containerization of a substantial legacy Ruby on Rails application, comprising over 300 EC2 instances. Utilized \textbf{Kubernetes}, \textbf{Helm}, and \textbf{Flux} to ensure seamless deployment, resulting in enhanced scalability and performance for critical services.}
        \item {Collaborated within an engineering cohort to migrate on-premise Kubernetes clusters out of support to the latest versions utilizing KubeSpray, ensuring ongoing security, stability, and compliance}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Principle DevOps Engineer - Contract} % Job title
  %   {Vybera Wallet} % Organization
  %   {Netherlands, Remote} % Location
  %   {Aug. 2021 - Dec. 2021} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Working with TopTal, myself and a team of 10 contractors were bought together to build a non-custodial \textbf{cryptocurrency} wallet}
  %       \item {Bootstraped \textbf{React}, \textbf{React Native} and \textbf{Electron} projects before any developers started working on the project such that they could get started from day one}
  %       \item {Used \textbf{GitHub Actions} to build, text and deployments pipelines for Windows, Linux, MacOS, Android and iOS}
  %       \item {Helped to implement the Ethereum blockchain using \textbf{Web3.js} and \textbf{Ethers.js} to interact with the blockchain}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  % \cventry
  %   {DevOps Consultant - Contract} % Job title
  %   {Canopy Servicing} % Organization
  %   {Haiwaii, United States - Remote} % Location
  %   {Jan. 2020 - Sept. 2020} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Hired as the first engineering employee to help the founders architect their application and build their AWS estate}
  %       \item {Dramatically increased the speed of development by introducing the \textbf{serverless.com} framework enabling the application to be put in front of potential customers and VC's more quickly}
  %       \item {Built a scalable proof of concept for calculating interest rates using \textbf{AWS Step Functions} with \textbf{TypeScript} and \textbf{Postgres}}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  \cventry
    {DevOps Lead Engineer - Digital Cloud} % Job title
    {Dyson} % Organization
    {Bristol, United Kingdom} % Location
    {Nov. 2018 - April. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead Engineer for the Digital Cloud Infrastructure Team tasked to architect and implement cloud infrastructure with a strong focus on \textbf{Infrastructure as Code} with \textbf{Terraform} and \textbf{Ansible} primarily in \textbf{AWS} and \textbf{Azure} for over 30 accounts and 20 applications}
        \item {Created a private Terraform Data Source to get AWS Active Directory properties in \textbf{Go}}
        \item {Designed and implemented a common framework for \textbf{Docker} services in \textbf{AWS ECS/Fargate}}
        \item {Increased the velocity of application deployment by building \textbf{CI/CD} pipelines allowing developers and QA to run short-lived environments based on \textbf{Git} features branches}
        \item {Decreased deployment time by removing manual steps and reliance on an individual’s knowledge with \textbf{Team City}, \textbf{Octopus} and \textbf{Jenkins}}
        \item {Lead initiative on a multi account strategy allowing for the automated network provisioning of hundreds of AWS accounts using \textbf{Direct Connect} and \textbf{Transit Gateway}}
        \item {Built an application with \textbf{Node.js} allowing for global markets to create their own SEO redirects in \textbf{Akamai} for marketing promotions}
        \item {Reduced AWS costs by implementing scaling patterns based on traffic and workload, rightsizing instances and ensuring that resources are cleaned up properly by decommissioning tooling}
        \item {Operated in bi-weekly sprints, participating in an array of agile ceremonies (\textbf{Jira and Confluence})}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {DevOps \& Engineering Team Leader} % Job title
    {Eloquent Technologies} % Organization
    {Taunton, United Kingdom} % Location
    {Oct. 2016 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Ensured uptime of cloud services through network upgrades, maintaining and supporting multi-DC VMWare platforms and managing Linux and Windows servers. (Hands-on and \textbf{Puppet})}
        \item {Designed and implemented Laravel based API backends with \textbf{Vue.js} based frontends for a variety of software development projects. Deployed with bespoke \textbf{CI/CD pipelines in Docker}}
        \item {Automated \textbf{Cisco} networking devices (NXOS/IOS) for layer 2 and layer 3 configurations including \textbf{BGP and MPLS}}
        \item {Acted as the primary escalation point for 1st/2nd line teams, responsible for the support and sometimes provisioning of customers IT infrastructures}
        \item {Built relationships with a mixed customer base all with their own unique requirements and levels of technical awareness from PLC's to one-man-bands  }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Administrator} % Job title
    {A.H Warren Trust Ltd} % Organization
    {Crewkerne, United Kingdom} % Location
    {Jul. 2014 - Sept. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Sole System Administrator for 40 person organisation}
        \item {Automated monotonous day to day administration tasks with \textbf{Powershell}}
        \item {Replaced an ageing physical server infrastructure with a hybrid one using on-premise resource (\textbf{VMWare, Hyper-V}) and cloud resource (\textbf{Azure}) for a mixture of \textbf{Linux and Windows} applications}
        \item {Increased efficiency by creating RESTful API's (\textbf{Node.JS}) to automate labour intensive tasks and display key performance metrics to directors}
        \item {Enforced consistent state on networking devices using configuration management tools (\textbf{Ansible})}
        \item {Maintained and supported a Microsoft Dynamics AX 2012 ERP platform}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software and Support Engineer} % Job title
    {CFB Solutions Ltd} % Organization
    {Crewkerne, United Kingdom} % Location
    {Feb. 2013 - Jul. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Team leader for a small team responsible for delivering managed services to customers within Windows Server and Desktop environments}
        \item {Accommodated the core network for a wireless internet service provider offering network 50+ residential and commercial properties}
        \item {Developed a bespoke help desk system using C\# and \textbf{JavaScript} frameworks}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
